Read quality check

### 2019-06-10 writing/tech_compare.Rmd
Change titles so everything fits on the page

# IonTorrent ITS2 ASVs: coverage by PacBio long reads
```{r}
asv_table %>%
  arrange(desc(is_057)) %>%
  filter(is_057 > 0) %>%
  ggplot(aes(y = is_057, x = seq_along(is_057), fill = pb_500 > 0)) +
  geom_col(width = 1) +
  xlab("ASVs") +
  ylab("reads") +
  scale_fill_discrete(name = "PacBio") +
  scale_y_continuous(sec.axis = sec_axis(~ ./sum(.), name = "frac. of comm."))
```
`r asv_table %>% filter(is_057 > 0) %>% {formatC(sum(.$pb_500 > 0) / length(.$is_057)*100, digits = 1, flag = "0", format = "f")}`% of IonTorrent ASVs (`r asv_table %>% {formatC(sum(.$is_057[.$pb_500 > 0]) / sum(.$is_057) * 100, digits = 1, flag = "0", format = "f")}`% of reads) also include at least one PacBio read.

# IonTorrent ITS2 ASV-OTUs: coverage by PacBio long reads
```{r}
otu %>%
  arrange(desc(is_057)) %>%
  filter(is_057 > 0) %>%
  ggplot(aes(y = is_057, x = seq_along(is_057), fill = pb_500 > 0)) +
  geom_col(width = 1) +
  xlab("OTUs") +
  ylab("reads") +
  scale_fill_discrete(name = "PacBio") +
  scale_y_continuous(sec.axis = sec_axis(~ ./sum(.), name = "frac. of comm."))
```
`r otu %>% filter(is_057 > 0) %>% {formatC(sum(.$pb_500 > 0) / length(.$is_057)*100, digits = 1, flag = "0", format = "f")}`% of IonTorrent OTUs (`r otu %>% {formatC(sum(.$is_057[.$pb_500 > 0]) / sum(.$is_057) * 100, digits = 1, flag = "0", format = "f")}`% of reads) also include at least one PacBio ASV.

>>>>

# IonTorrent ITS2 ASVs: coverage by long PacBio
```{r}
asv_table %>%
  arrange(desc(is_057)) %>%
  filter(is_057 > 0) %>%
  ggplot(aes(y = is_057, x = seq_along(is_057), fill = pb_500 > 0)) +
  geom_col(width = 1) +
  xlab("ASVs") +
  ylab("reads") +
  scale_fill_discrete(name = "PacBio") +
  scale_y_continuous(sec.axis = sec_axis(~ ./sum(.), name = "frac. of comm."))
```
`r asv_table %>% filter(is_057 > 0) %>% {formatC(sum(.$pb_500 > 0) / length(.$is_057)*100, digits = 1, flag = "0", format = "f")}`% of IonTorrent ASVs (`r asv_table %>% {formatC(sum(.$is_057[.$pb_500 > 0]) / sum(.$is_057) * 100, digits = 1, flag = "0", format = "f")}`% of reads) also include at least one PacBio read.

# IonTorrent ITS2 ASV-OTUs: coverage by long PacBio
```{r}
otu %>%
  arrange(desc(is_057)) %>%
  filter(is_057 > 0) %>%
  ggplot(aes(y = is_057, x = seq_along(is_057), fill = pb_500 > 0)) +
  geom_col(width = 1) +
  xlab("OTUs") +
  ylab("reads") +
  scale_fill_discrete(name = "PacBio") +
  scale_y_continuous(sec.axis = sec_axis(~ ./sum(.), name = "frac. of comm."))
```
`r otu %>% filter(is_057 > 0) %>% {formatC(sum(.$pb_500 > 0) / length(.$is_057)*100, digits = 1, flag = "0", format = "f")}`% of IonTorrent OTUs (`r otu %>% {formatC(sum(.$is_057[.$pb_500 > 0]) / sum(.$is_057) * 100, digits = 1, flag = "0", format = "f")}`% of reads) also include at least one PacBio ASV.
